\section{Code Listings}

\sourcecode{figures/probe-output}{fig:probe-output}{
  The raw XML output of issuing the Probe command to the Test
  Agent by fetching from the URL \texttt{\agenturl/probe}.  The lines
  are numbered for reference only; the line numbers aren't part of the
  actual XML output.}

\sourcecode{figures/current-output}{fig:current-output}{
  The raw XML output of issuing the Current command to the Test
  Agent without any arguments. You can see this by pointing a Web
  browser at \texttt{\agenturl/probe}.  The lines
  are numbered for reference only; the line numbers aren't part of the
  actual XML output.}

\sourcecode{figures/helloworld.cs}{fig:code:helloworld}{
  Simple C\# program
  that allows user to specify a component type 
  and name, and repeatedly calls the Current command to get a new
  snapshot of samples and then extracts the measurement value(s) from
  the desired component out of each set of samples.}

\sourcecode{figures/helloworld-output}{fig:code:helloworld-output}{
  Example output from the simple program in figure~\ref{fig:code:helloworld}.}

\sourcecode{figures/helloworld2.cs}{fig:code:helloworld2}{
  Given user-specified sample criteria, collect a number of samples of
  and export them to a Comma-Separated Values (CSV) file, for possible
  import into a database or spreadsheet.}

\sourcecode{figures/MTConnect.cs}{fig:code:mtconnect-api}{
  The MTConnect namespace, classes and methods provided by CLUE 1.0 for
  Microsoft .NET Framework.  The class descriptions are given using C\#
  syntax but translation to other object-oriented 
  .NET languages is straightforward.}

\sourcecode{figures/MTCEvent.cs}{fig:code:mtconnect-event}{
  The definition of an MTConnect Event provided by CLUE 1.0 for
  Microsoft .NET Framework.
}

\sourcecode{figures/spiral.ngc}{fig:code:spiral}{
  An elided version of the GCode program continuously running on the
  \mtc{} Test Agent (line numbers added).  It repeatedly cuts a spiral pattern.
}
